---
title: "Analysing female representation in digital historical 4X games"
author:
  - Sophie C. Schmidt:
      email: s.c.schmidt@uni-koeln.de
      institute: [DAI]
      correspondence: true
  - Tine Rassalle:
      email: tinerassalle@hotmail.com 
      institute: [UNCCH]
      correspondence: false
institute:
  - DAI: Deutsches Arch채ologisches Institut
  - UNCCH: University of North Carolina at Chapel Hill
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

<!-- With the following code you can access and display values from the yml header above. -->

Keywords: `r rmarkdown::metadata$keywords`

Highlights: `r rmarkdown::metadata$highlights`

<!-- The following code chunk defines some general settings how code chunks should behave. -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```

<!-- The actual document text starts here: -->

# load data

```{r}
leaders <- readODS::read_ods("../data/raw_data/female_leaders_2020-10-14.ods")

```

# leader ratios time series analysis

```{r}
library(ggplot2)
library(dplyr)


ggplot(data = leaders) +
  geom_point(aes(x = release_date,
             y = nr_female_leaders), 
             col = "green")+
  geom_line(aes(x = release_date,
             y = nr_female_leaders), 
             col = "green")+
    geom_point(aes(x = release_date,
             y = nr_male_leaders), 
             col = "blue")+
  geom_line(aes(x = release_date,
             y = nr_male_leaders), 
             col = "blue")

```

Daten umformen, so dass entsteht:

 * Verh채ltniswert Frauen / M채nner + Frauen
 * kumulativ zusammengerechnet f체r jede Spiel (original + erweiterungen)


```{r}

leaders2 <- readODS::read_ods("../data/raw_data/female_leaders_2020-10-15.ods")

leaders2$ratio <- leaders2$nr_female_leaders / (leaders2$nr_female_leaders + leaders2$nr_male_leaders)

library(dplyr)
library(magrittr)
library(stringr)
library(ggrepel)

dates <- leaders2 %>%
  filter(str_detect(expansion, 'original'))%>%
  use_series(release_date)

leaders2 %>%
  arrange(release_date)%>%
  group_by(game) %>%
  mutate(sum_ratio = cumsum(nr_female_leaders)/(cumsum(nr_male_leaders)+ cumsum(nr_female_leaders)))%>%
  ggplot(aes(x = release_date,
             y = sum_ratio,
             col = series,
             label = game))+
    geom_hline(yintercept = 0.0)+
   geom_hline(yintercept = 0.5, linetype = "dashed")+
  geom_point()+
  geom_line(aes(linetype = game)) +
  geom_label_repel(data = . %>% filter(str_detect(expansion, 'original')) %>% filter(str_detect(game, 'Civ')),
                  size          = 4,
                  box.padding   = 0.5,
                  point.padding = 0.5,
                  line.padding  = 0.5,
                  force         = 100,
                  segment.size  = 0.2,
                  nudge_y       = 0.2)+
    geom_label_repel(data = . %>% filter(str_detect(expansion, 'original')) %>% filter(str_detect(game, 'Age')),
                  size          = 4,
                  box.padding   = 0.5,
                  point.padding = 0.5,
                  force         = 100,
                  segment.size  = 0.2,
                  nudge_y       = -0.2)+
  theme_minimal()+
  ggtitle("Ratio of female AI leaders per game", subtitle = "with later expansions")+
  guides(linetype = FALSE)+
  scale_x_date(expand = expansion(mult = c(0.2, .2)),
               name = "release date") +
  scale_y_continuous(expand = expansion(mult = c(0.2, .2)),
                     name = "cumulative ratio",
                     breaks = seq(0.0, 0.6, 0.1))

ggsave("../figures/leaders_cumulative.png", dpi = 300)

```


Absolute Zahlen ausprobieren:

```{r}

leaders2 %>%
  arrange(release_date)%>%
  group_by(game) %>%
  mutate(sum_female = cumsum(nr_female_leaders))%>%
    mutate(sum_male = cumsum(nr_male_leaders))%>%
  ggplot(aes(x = release_date,
             col = series,
             label = game))+
  geom_point(aes(y = sum_female))+
  geom_line(aes(y = sum_female)) +
    geom_point(aes(y = sum_male,
                   alpha = 0.7))+
  geom_line(aes(y = sum_male,
                alpha = 0.7))+
  facet_grid(~game)
  
geom_label_repel(data = . %>% filter(str_detect(expansion, 'original')) %>% filter(str_detect(game, 'Civ')),
                  size          = 4,
                  box.padding   = 0.5,
                  point.padding = 0.5,
                  line.padding  = 0.5,
                  force         = 100,
                  segment.size  = 0.2,
                  nudge_y       = 0.2)+
    geom_label_repel(data = . %>% filter(str_detect(expansion, 'original')) %>% filter(str_detect(game, 'Age')),
                  size          = 4,
                  box.padding   = 0.5,
                  point.padding = 0.5,
                  force         = 100,
                  segment.size  = 0.2,
                  nudge_y       = -0.2)+
  theme_minimal()+
  scale_x_date(expand = expansion(mult = c(0.2, .2)),
               name = "Release Date") +
  scale_y_continuous(expand = expansion(mult = c(0.2, .2)),
                     name = "Ratio of female AI leaders",
                     breaks = seq(0.0, 0.6, 0.1))




```


# Characters

```{r}
charas <- readODS::read_ods("../data/raw_data/female_charas_2020-10-14.ods")


library(dplyr)
library(ggplot2)
library(magrittr)

safe_colorblind_palette <- c( "#CC6677", "#DDCC77", "#117733", "#332288", "#AA4499", 
                             "#44AA99", "#999933", "#882255", "#661100", "#6699CC", "#888888")

colorblind_palette9 <- c("#88CCEE", "#CC6677", "#DDCC77", "#117733", "#332288", "#44AA99", "#999933", "#882255", "#661100", "#6699CC", "#888888")

charas %>%
  count(figure_standardized, culture)%>%
  #group_by(figure_standardized) %>%          # now required with changes to dplyr::count()
  filter(n > 1)%>%
  ggplot()+
  geom_col(aes(x = reorder(figure_standardized, n),
               y = n,
               fill = culture))+
  xlab("named figures")+
  ylab("number of mentions")+
  scale_fill_manual(breaks = c("Spain", "England", "China", "Egypt", "Russia", "Celts", "Ethiopian", "all", "Byzantine", "France", "Amazones (Incas)"),
                    values = colorblind_palette9)+
  theme_bw()+
  coord_flip()
  
ggsave("../figures/named_women.png", dpi = 300)  
```


<!-- The following line inserts a page break  -->

\newpage

# References 

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

<div id="refs"></div>

\newpage

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies: 

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
